{\bf Simulating a two dimensional particle in a square quantum box with CUDA}

### 2013-08-17 paper/paper.tex
Created probability and particle-creation functions in code Added documentation to these functions in the paper Added conventions used to the paper

\section{Implementation}
    \subsection{Memory Management}
    \subsection{Optimizations}
    \subsection{Implementations Details}

>>>>

\section{Implementation}
    \subsection{Conventions}
    Some of the conventions adopted through the code are
    \begin{itemize}
        \item words in function and struct names are seperated by an \_ (underscore)
        \item words in variable names are glued together with the first letter
              capitalized. Except in the case of the first character.
        \item functions that start with \_ are helper functions
              and should not be used directly. They may be considered like private
              methods and properties in object-oriented code. No major documentation
              is provided for these functions and the author only uses inline code
              comments to document them
        \item Tiny mathematical and physical constants, such as $\hbar$ are expressed
              as float numbers without their orders. For example $\hbar = 1.054\cdot10^{-34}$
              is defined the following way \texttt{\#define HBAR 1.054 // without e-34}
    \end{itemize}

\newpage
\section{API}
    \subsection{Structs}
        \subsubsection{\texttt{\_wave\_function}}
        This struct is used by the \texttt{particle} struct and describes a wave function
        \begin{itemize}
            \item \texttt{int n} the energy level of the particle described by the wave function
            \item \texttt{float energy} the energy of the particle at that energy level
        \end{itemize}
        \subsubsection{\texttt{particle}}
        This struct represents a particle and have the following elements
        \begin{itemize}
            \item \texttt{float mass} the mass of the particle
            \item \texttt{\_wave\_function* wave} the wave function that describes the state of
                  the particle
        \end{itemize}

    \subsection{Functions}
        \subsubsection{\texttt{create\_particle}}
        This function is used to create a new particle.
        \begin{verbatim}
void create_particle(particle* p, int n, float mass);
        \end{verbatim}
        \begin{itemize}
            \item \texttt{particle* p} the particle to create
            \item \texttt{int n} the energy level of the particle
            \item \texttt{float mass} the mass of the particle
        \end{itemize}
        \subsubsection{\texttt{probability}}
        This function finds the probability of finding the particle in the box of center $(x, y)$
        and of dimensions $\epsilon$x$\epsilon$\\
        The function returns a \texttt{float}; the probability of finding the particle at points (x, y)
        \begin{verbatim}
float probability(particle *p, float x, float y);
        \end{verbatim}
        \begin{itemize}
            \item \texttt{particle* p} the particle to find the probability of
            \item \texttt{float x} the x-coordinate of the center of the box 
            \item \texttt{float y} the y-coordinate of the center of the box
        \end{itemize}
